Compare pseqs

### 2019-05-15 comparepseqs.Rmd
Different rds location

dir.create("rds/", showWarnings = FALSE)
dir.create("session/", showWarnings = FALSE)
```

@@

    if("clean" %in% names(args)) {
        unlink("rds", recursive=TRUE)
        unlink("cache", recursive=TRUE)
    }
    if ("loadlast" %in% names(args) )
        load(paste0("session/", sort(list.files("session"), decreasing = TRUE)[1]))
}
```

@@

```{r matrix calculation}
if (!file.exists("rds/comparepseqs_bray_matrix.rds")) {
    bray.dist.matrix <- mclapply(pseq, function(x) calculate.beta.matrix(x), mc.cores = 4)
    saveRDS(bray.dist.matrix, file = "rds/comparepseqs_bray_matrix.rds")
} else {
    bray.dist.matrix  <- readRDS("rds/comparepseqs_bray_matrix.rds")
}
```

>>>>

dir.create("rds-comparepseqs/", showWarnings = FALSE)
dir.create("session/", showWarnings = FALSE)
```

@@

    if("clean" %in% names(args)) {
        unlink("rds-comparepseqs", recursive=TRUE)
        unlink("cache", recursive=TRUE)
    }
    if ("loadlast" %in% names(args) )
        load(paste0("session/", sort(list.files("session"), decreasing = TRUE)[1]))
}
```

@@

```{r matrix calculation}
if (!file.exists("rds-comparepseqs/comparepseqs_bray_matrix.rds")) {
    bray.dist.matrix <- mclapply(pseq, function(x) calculate.beta.matrix(x), mc.cores = 4)
    saveRDS(bray.dist.matrix, file = "rds-comparepseqs/comparepseqs_bray_matrix.rds")
} else {
    bray.dist.matrix  <- readRDS("rds-comparepseqs/comparepseqs_bray_matrix.rds")
}
```
